Searching for flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2022-12-28 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Orbital coherence times}

@@

>>>>

\subsection{Period coherence times}

@@

\begin{figure*}[ht!]
    \script{paper_coherence_histogram.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PAPER_coherence_histogram.png}
        \caption{
           Time span of observation vs. coherence time or the orbital and rotational periods, respectively. Orbital periods are all known precisely enough, so that the phase uncertainty at the last observed flare is of the order of $10^{-2}$. In contrast, in stars with known rotation periods, the precision is often too low, so that the phase of the last flare is often undetermined (ratio on x-axis $\sim 1$.
        }
        \label{fig:coherence_hist}
    \end{centering}
\end{figure*}
